\documentclass{src/resume} % Use the custom resume.cls style
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Franco Brunetta Pan}
\address{+1(437) 243\-5239 \\ Toronto, ON} 
\address{
    \href{mailto:job@fr-an.co}{job@fr-an.co} \\ 
    \href{https://linkedin.com/in/francopan}{linkedin.com/in/francopan} \\ 
    \href{www.francopan.com.br}{www.francopan.com.br}
} 

\begin{document}

    \begin{rSection}{OBJECTIVE}
        {FullStack Software Developer with 7+ years of experience. Experience in managing a team of developers, providing customer support and programming real-time systems with large databases. Knowledge and work experience of traditional and agile processes. Looking for contract or fulltime.}
    \end{rSection}

    \begin{rSection}{Education}
        {\bf Bachelor of Computer Science}, Universidade de Caxias do Sul \hfill {Expected 2023}
    \end{rSection}

    \begin{rSection}{SKILLS}
        \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
            Technical Skills & Java, SpringBoot, Hibernate, Javascript, Typescript, Angular, Docker\\
            Soft Skills & Leadership, TeamWork, Creativity, Integrity, Planning, Communication\\
            Other & Git, Jenkins, Maven, Node, Jira, Confluence, Scrum, SVN, Postgres, MSSQL
        \end{tabular}\\
    \end{rSection}

    \begin{rSection}{EXPERIENCE}
        \textbf{Web Designer (Front-End Developer)} \hfill Aug 2020 \- Jan 2023\\
        TrustArc Inc. \hfill \textit{Toronto, ON, Canada}
        \begin{itemize}
            \itemsep -3pt {}
            \item Programmed UI app for Integrations platform using Angular, HTML, Typescript, Javascript, SCSS. 
            \item Improved page loading time of legacy application by over 100\%.
        \end{itemize}
        \textbf{Development Manager} \hfill Mar 2017 \- Aug 2020\\
        Codi Sistemas de Gestão da Produção \hfill \textit{Caxias do Sul, RS, Brazil}
        \begin{itemize}
            \itemsep -3pt {} 
            \item Managed a team of 5 to develop and maintain an entreprise size application.
            \item Developed Back-end using Java, SpringBoot, Hibernate, Liquibase.
            \item Developed Front-end using Angular, HTML, Typescript, Javascript, SCSS.
            \item Introduced Agile methodologies using Scrum, Planning Poker and Kanban.
            \item Improved time and delivery estimation accuracy by 50\%.
            \item Implemented a CI/CD pipeline with Jenkins, Docker, Nexus, Gitlab, Jira.
        \end{itemize}
    \end{rSection} 

    \begin{rSection}{PROJECTS}
        \vspace{-1.25em}
        \item \textbf{Delivery Estimation} {Built a tool to provide a confidence table on how many sprints a project/epic will be done based on montecarlo and past sprints data. \href{https://francopan.com.br/project/montecarlo-estimation/}{Click to see project}}
        \item \textbf{MovieDB UI} {Built a project for an alternative UI for \href{https://themoviedb.org/}{TheMovieDB} using my skills with Angular, CSS, HTML and Docker}. \href{https://francopan.com.br/project/moviedb-ui/}{Click to see project.}
        \item \textbf{Industrial System} {This was a project created under my time at Codi. It was a SaaS Manufacturing Execution System targeted at small companies. Designed the System Architecture and wrote the base/core projects for APIs with Java, Hibernate, Liquibase, SpringBoot and UI with Angular.}  \href{https://francopan.com.br/project/industrial-system/}{Click to see project.}
    \end{rSection}

    \begin{rSection}{Extra-Curricular Activities}
        \begin{itemize}
            \item 	Write \href{https://francopan.com.br/blog-posts/}{blog posts} about topics in tech. 
            \item	Actively participating in tech conferences, meetups and courses.
        \end{itemize}
    \end{rSection}

\end{document}